### 2011-10-30 doc/theses/vitasek/chapter-3-mip.tex
Thesis: in progress.

In GLPK \textit{MathProg} language, this translates to the following formulation. % TODO cite mathprog

@@

\section{Heuristics}

@@

% TODO od I need to specify which are my own idea? I guess so, I should link any heu that is not mine. But do I need to stress that for example Fuzzy is mine?

@@

This is again a rather trivial diversification improvement heuristic. By removing a random subset of specified size from each solution in the pool, it provides the variability needed to escape from local optima. % TODO make sure we have talked about local optima before

@@

\heu{Hungry} tries to improve each solution in the feasible pool in the following way. It orders all candidate AMs not present in the solution by decreasing weight. Afterwards, it iteratively tries to extend the solution with these AMs, taking care not to violate the ID set condition. The resulting solution (whether any AMs were added or not) is then returned to the pool. This is then intensification, and Listing \ref{listing-ih-hungry} captures the process.

@@

@@

Once an ID set is found, regardless of how exactly, it is easy to find the IDREF set, i.e. the attribute mappings that can be declared as IDREF. % TODO link FIDAX, they did it first.

First of all, from the set of all the attribute mappings in the model remove all the AMs contained in the ID set. This is because the specification % TODO link to the specific anchor in the page
does not allow an attribute to be ID and IDREF (IDREFS) at the same time. Let us denominate these mappings as \textit{IDREF candidates} (obviously different from \textit{candidate AMs}). % TODO link candidate AMs

>>>>

In GLPK \textit{MathProg} language (see \cite{mathprog}), this translates to the following formulation.

@@

\section{Heuristics}
\label{section-mip-heuristics}

@@

@@

This is again a rather trivial diversification improvement heuristic. By removing a random subset of specified size from each solution in the pool, it provides the variability needed to escape from local optima in the solution space.

@@

\heu{Hungry} tries to improve each solution in the feasible pool in the following way. It orders all candidate AMs not present in the solution by decreasing weight. Afterwards, it iteratively tries to extend the solution with these AMs, taking care not to violate the ID set condition. The resulting solution (whether any AMs were added or not) is then returned to the pool. This is then intensification, and Listing \ref{listing-ih-hungry} captures the process.\\

@@

The following three IHs: \heu{Mutation}, \heu{Crossover} and \heu{Local Branching} are inspired by \cite{heu-lecture}.

@@

Once an ID set is found, regardless of how exactly, it is easy to find the IDREF set, i.e. the attribute mappings that can be declared as IDREF. This algorithm is adopted from \cite{fidax}.

First of all, from the set of all the attribute mappings in the model remove all the AMs contained in the ID set. This is because the specification of DTD/XSD does not allow an attribute to be ID and IDREF (IDREFS) at the same time. Let us denominate these mappings as \textit{IDREF candidates} (obviously different from \textit{candidate AMs}).

### 2011-10-30 doc/theses/vitasek/chapter-4-1-experiments-setup.tex
Thesis: in progress.

To understand our test data sets we discuss their origin and \textit{graph representation}. As mentioned earlier, % TODO link
the problem of finding the optimal ID set is in fact the problem of finding the maximum weighted independent set in a graph. Therefore it is interesting to actually see the graphs of these data sets and understand some related metrics.

@@

This approach is useful, because as stated in TODO link, ID attributes are a special case of XML keys. We can use this approach to find XML keys: convert some ``suspicious" data into attributes, find the optimal ID set and then create XML key based on this ID set.

@@

\begin{figure}
  \caption{Artificial data}
  \label{image-experiments-data-artificial}
  \centering
  	\subfigure[\dataset{48-80}]{\includegraphics[width=\textwidth]{images/experiments/data/artificial/size/40-80}}
	\subfigure[\dataset{70-245}]{\includegraphics[width=\textwidth]{images/experiments/data/artificial/size/70-245-fixed}}
\end{figure}

>>>>

To understand our test data sets we discuss their origin and \textit{graph representation}. As mentioned earlier in Chapter \ref{chapter-mip}, the problem of finding the optimal ID set is in fact the problem of finding the maximum weighted independent set in a graph. Therefore it is interesting to actually see the graphs of these data sets and understand some related metrics.

@@

This approach is useful, because as mentioned in Chapter \ref{chapter-research}, ID attributes are a special case of XML keys. We can use this approach to find XML keys: convert some ``suspicious" data into attributes, find the optimal ID set and then create XML key based on this ID set.

@@

\begin{figure}
  \caption{Artificial data}
  \label{image-experiments-data-artificial}
  \centering
  	\subfigure[\dataset{48-80}]{\includegraphics[width=\textwidth]{images/experiments/data/artificial/size/40-80}}
	\subfigure[\dataset{70-245}]{\includegraphics[width=.9\textwidth]{images/experiments/data/artificial/size/70-245-fixed}}
\end{figure}
